IFC Inside: A General Approach to Retrofitting Languages with Dynamic Information Flow Control

### 2014-07-08 paper/real.tex
Mention web workers
Signed-off-by: Edward Z. Yang <ezyang@cs.stanford.edu>

Most notably, tasks in COWL usually correspond to browsing contexts,
such as iframes.
%
Hence, the global object |tS0| also contains the DOM, the
\verb|XMLHttpRequest| (XHR) object, etc.
%
To ensure that JavaScript code cannot communicate using these objects
(e.g., to the network with XHR or persistent storage using the DOM),
COWL additionally uses content security policy (CSP)~\cite{csp1.1}.\footnote{
  Since CSP does not yet restrict message-passing or navigation, this
  was addressed explicitly.
}
%
Note, that this does not prevent tasks from manipulating the DOM
(e.g., to render information).
%
Rather, to enforce task-isolation, external effects due to DOM access
are suppressed.

Simply disallowing all external effects for all browsing contexts is
overly-restricting; pages typically load images, perform XHR requests,
etc.
%
Hence, rather than disallowing all external effects, COWL allows
controlled network communication (inter-frame communication is
dictated by our |send| rule) by associating an implicit label with a
remote host: namely the label corresponding to its origin.
%
In turn, when a task perform a request, the COWL runtime performs the
same label check as that of |send|, e.g., does the task label flow to
the remote origin label.

>>>>

Tasks in COWL usually correspond to browsing contexts, such as iframes,
where the global object |tS0| also contains the DOM, the
\verb|XMLHttpRequest| (XHR) object, etc.
%
Existing browser APIs also offer \emph{web workers}, which can
be spawned by JavaScript code and have
the same isolation properties as tasks in our system.
%
The isolation of web workers was motivated by the lack of multithreading
in JavaScript; however, their isolation properties are equally useful for information
flow control.

To ensure that JavaScript code cannot communicate using these objects
(e.g., to the network with XHR or persistent storage using the DOM),
COWL additionally uses content security policy (CSP)~\cite{csp1.1}.\footnote{
  Since CSP does not yet restrict message-passing or navigation, this
  was addressed explicitly.
}
%
Note, that this does not prevent tasks from manipulating the DOM
(e.g., to render information), so external effects due to DOM access
are also suppressed.
%
Simply disallowing all external effects for all browsing contexts is
overly-restricting; pages typically load images, perform XHR requests,
etc.
%
Hence, COWL allows
controlled network communication (inter-frame communication is
dictated by our |send| rule) by associating an implicit label with a
remote host: namely the label corresponding to its origin.
%
In turn, when a task perform a request, the COWL runtime performs the
same label check as that of |send|, e.g., does the task label flow to
the remote origin label.
